disaggregation: An \proglang{R} package for Bayesian spatial disaggregation modelling

### 2019-11-21 article.Rnw
Not sure but its weird having api in the code without some explanation.
Line length. But yes we definitely need to describe api.

In this section we show how to use the \pkg{disaggregation} package using a dataset of aggregated malaria case counts across Madagascar. Malaria is an infectious disease caused by parasites of the \emph{Plasmodium} group, transmitted by \emph{Anopheles} mosquitoes. Malaria transmission is therefore closely related to mosquito and parasite development. Environmental factors such as temperature, rainfall and elevation have been shown to have signifcant effect on mosquito survival and development; in general mosquitoes favour warm, humid environments with moderate rainfall. Therefore, such environmental covariates would be useful in a malaria disaggregation model to inform fine-scale distributions. In this model we use the environmental covariates of mean land surface temperature (LST), variation in LST, elevation, and enhanced vegetation index (EVI) to inform spatial heterogeneity in malaria risk. These covaraites are obtained from the Moderate Resolution Imaging Spectroradiometer (MODIS), which provides many measurements over the entire Earth's surface (\url{https://modis.gsfc.nasa.gov/data/}).

@@

# Add incidence information to the shapefile (incidence = API * population/1000)
indices <- match(shapes$ID_2, as.character(api$fdef_id))
shapes$inc <- (api$api_mean_pf[indices] * api$pop_at_risk_pf[indices])/1000

>>>>

In this section we show how to use the \pkg{disaggregation} package using a dataset of aggregated malaria case counts across Madagascar. Malaria is an infectious disease caused by parasites of the \emph{Plasmodium} group, transmitted by \emph{Anopheles} mosquitoes. Malaria transmission is therefore closely related to mosquito and parasite development. Environmental factors such as temperature, rainfall and elevation have been shown to have signifcant effect on mosquito survival and development; in general mosquitoes favour warm, humid environments with moderate rainfall. Therefore, such environmental covariates would be useful in a malaria disaggregation model to inform fine-scale distributions. In this model we use the environmental covariates of mean land surface temperature (LST), variation in LST, elevation, and enhanced vegetation index (EVI) to inform spatial heterogeneity in malaria risk. These covaraites are obtained from the Moderate Resolution Imaging Spectroradiometer (MODIS), which provides many measurements over the entire Earth's surface (\url{https://modis.gsfc.nasa.gov/data/}). 
Malaria incidence rate is often given per thousand cases and given the term annual parasite index (API).

@@

# Add incidence information to the shapefile 
# (incidence count = API * population/1000)
indices <- match(shapes$ID_2, as.character(api$fdef_id))
shapes$inc <- (api$api_mean_pf[indices] * api$pop_at_risk_pf[indices])/1000
